The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2016-08-23 reviews/2016-07-response-to-reviewers.tex

\answerok{We thoroughly reworked the general grounding and flow of the manuscript. In particular:
\itx{
\x We believe that the introductory parts provide a clearer presentation of our question and how it relates to existing literature (including the areas we overlooked) and hypotheses
\x The new ``Discussion'' section, which was indeed missing, should properly reconnect our results to the related works introduced at the beginning of the paper.
}

Finally, several modifications in the ``Results'' section (more examples, a short discussion of the distance traveled by substitutions on the synonym network in footnote \#15, and the addition of the second null hypothesis $\mathcal{H}_{00}$ in the ``Variation'' subsection) should better describe the type of changes undergone by quotes.
}

\critique{The experiment design also has some substantial flaws. First, some crucial factors were not considered - most notably, part of speech. I suspect, for instance, that pronouns and other closed-class words are less often substituted than open-class words.  Phonological neighborhood density could also be important, though probably less so.  Second, no analysis was done that included all of the factors in, e.g., a multi-feature regression model.  While the features being considered are not strongly correlated, they are still likely to interact - especially if part-of-speech is added.  Third, the restriction to single-word substitutions introduces some significant confounds.  I'm not convinced that correctly and incorrectly copying a quote should be viewed as separate behaviors.
}

\answerok{
We addressed these points in the revised version:
\itx{
\x We checked and discussed the susceptibility of part-of-speech (POS). While {a rigorous treatment of} the open-/closed-class question is largely precluded by our exclusion of stopwords from the analysis (which led us to not discuss that point in the manuscript), {the data does indeed indicate that closed class words are less substituted than open class words (the \emph{Closed class-like} category is mainly made of {closed class words})}. As the manuscript discusses however, this concerns less than 7\% of the substitutions we consider, and has likely no effect on our results.
\x Following this suggestion, we added phonological neighborhood density as a word feature. We show that it forms a subgroup of strongly correlated variables, together with orthographic neighborhood density, and choose the latter as a more natural representative of this subgroup given the task studied.
\x We introduced a multi-feature regression model to estimate variation upon substitution, showing that the magnitude of the variation of a feature is mainly predicted by the {start word's value for} that very feature, generally with negligible interaction with the other features (see also below and figure 8).
\x We expanded substitution models to {also detect quotes undergoing up to two substitutions}, which yielded the same results as single substitutions {(see below)}. 
}

@@

\critique{\itx{
\x needs a substantive discussion of the results}
}

\answerok{An entirely new ``Discussion'' section is now devoted to this task.}

\critique{\itx{
\x show that the phi value is capturing what it purports to capture
\x and that the factors aren't conflated with length
\x is the single-substitution biasing the data?
\x make sure that the reported measures are interpretable
\x if low-frequency words have 1/3 chance of being chosen as substitution (Fig. 4), what if there are four low-frequency words in a quote?
}
}

\answerok{{The measure we had proposed in the first version of the manuscript (for information, this was the subject of Fig. 4 in that manuscript) considered probabilities of substitutions as an aggregate quantity (and not at the individual sentence level).  It was difficult to use it to understand what happens when substitution occurs in a given sentence.}

{We therefore reworked the notion of susceptibility to make it more straightforward}. We now define it relatively to a null hypothesis: it measures the strength of a bias affecting a given feature value (i.e., how much a feature value is substituted compared to what it would be if targets were picked randomly). We present the corresponding results in Figs. 5 \& 6.

@@

\answerok{
These points should be addressed by the improved introduction. In particular regarding the last question, the new ``Discussion'' section additionally makes a connection with the iterated learning literature.
}

\critique{\itx{
\x what about the semantics of quote replication?
\x does part of speech influence substitution rate?
\x can you quantify the semantic distance between the original and substituted quote (e.g., get Mechanical Turkers to rate the semantic distance?)}
}

\answerok{We added a short discussion on the semantics of substituted quotes. We first aimed at quantifying the semantic distance by estimating the distance ``traveled'' by the substituted word in the WordNet hypernym-hyponym network as well as the FA network. This showed that substituted and substituting words are rarely direct synonyms, yet they usually achieve a similar meaning in the context of their sentence.
To further grasp the relationship of substitutions to synonyms we introduced a second null hypothesis in the ``Variation'' subsection, which compares the actual variation to what would happen if a random synonym of the start word were picked instead.

Finally, we also examined the effect of part-of-speech (POS): Fig. 5 details the results on five POS categories, {with a discussion of the corresponding effects in the main text, explaining} why we largely keep POS outside of our analysis.
}

@@

I understand that word-word metrics are not easily introduced in the type of analysis that the authors are attempting to do, where the analysis of the contributions of different global psycholinguistic variables are being weighed against each other. I just think that type of analysis is inappropriate here. Since the quotations were selected on the basis of single substitutions, it seems to me that the appropriate level of analysis is what properties of the word that is being substituted is the most predictive of the substitution. I suspect that the combination of frequency and semantic similarity will be by far the most predictive variables, consistent with past results on recall.
}

\answerok{The rewritten introductory sections of this revision now aim at explaining why we chose to use a feature-based analysis over the prediction of individual words (see below for more details about this).
Word-word similarity is now also shortly discussed in the beginning of the ``Results'' section (and in footnote \#15). We explored a number of other similarity measures provided by WordNet (based on paths in the WordNet network, or on similarity of Information Content extracted from external corpora), but none of them provided more insight than what is being discussed in that section.

{Regarding prediction, we would like to distinguish two questions. First, prediction of the actual disappearing and appearing words, which would be an extremely interesting result, but a prospect we believe to stand several steps away from what is currently possible.
As the revised introductory parts now allude to, the prediction of word intrusions is well mastered in the case of manually designed word lists but is not as exact in the case of random lists of words. Zaromb et al. (2006), for instance, predict the list from which prior-list intrusions come, but not the exact intruding word. To our knowledge, the prediction of intrusions in full sentences (either manually designed or not) has not been tackled. Finally, as explained in footnote \#3 and the ``Discussion'' section, our data set is ill-shaped to measure the accuracy of predictions we could make.}

{These reasons led us to focus on the second question: prediction of properties of the disappearing and appearing words. Indeed, Figs. 7 \& 10 provide average predictions of appearing word features given the properties of a disappearing word. We show that there are little to no interactions between word features (see Fig. 8), such that word frequency is not sufficient to predict variation of other features. Finally, we introduced a new null hypothesis ($\mathcal{H}_{00}$) in the ``Variation'' subsection which gives insight into how an appearing word relates to the synonyms of the word it replaces, and shows that appearing words are much more frequent than the average frequency of synonyms of the disappearing word.}

@@

\answerok{There are indeed very many possible models, yet we agree that a robustness check is also very sensible.  Substitution detection relies on a number of assumptions and we identified four binary parameters that differentiate potential models, such that the resulting 16 combinations cover most of the reasonable answers to inference uncertainties. We thus implemented, tested and checked these models, and we can report that our results remain valid for all 16 models (for the sake of clarity, we do not specifically report on these models, though).  \\

This leads to a much more detailed ``Substitution Model'' subsection which discusses these options along with the reference model we used throughout the paper.
}

\critique{ A second issue is the time spent on feature selection.  It is unclear why the authors do feature selection at all, as "the analysis is done on a per-feature basis."  It would again add to the robustness of their claims if they showed that all of the correlated features show the same pattern of susceptibility and bias in substitution.  In the same vein, it is not clear why the authors claim that age of acquisition, frequency, and number of synonyms have low levels of correlation "excluding the network properties".  Why would one ignore the correlations with the network features?
}

\answerok{Our feature selection step aims at making the results more intelligible. This section was indeed poorly written, and has been thoroughly revised to rationalize the process. In particular, we identify (six) groups of strongly correlated features (both manually by visual inspection and automatically with the help of an agglomeration algorithm, yielding identical results) and justify the choice of our six prototype features for each group.  Features belonging to the same group generally exhibit very similar behaviors across all measures (with few exceptions, notably number of phonemes and number of syllables {exhibiting less cognitive bias} than number of letters). Graphs produced for all features may be found at <https://huit.re/aEH77Gc3>, and could be included in a Supplementary Information bundle if requested.
}

### 2016-08-25 brains-protocol.tex
Remove spaces between panesl for manuscript formatting
fix/protocol: fix two typos

\begin{figure}[h]
    \centering
	\def\svgwidth{\linewidth}
	\small
	\input{images/substitution-unmodelled.pdf_tex}
	\caption{{\bf Possible paths from occurrence to occurrence.}
	\newtext{$q$, $q'$ and $q''$ are three quotation variants belonging to the same cluster.
	$q$ and $q''$ differ by two words, but $q'$ differs from both $q$ and $q''$ by a word.
	The second occurrence of $q$ can safely be considered a faithful copy of the first, but the occurrences of $q'$ and $q''$ are uncertain:
	while the first occurrence of $q'$ is most likely a substitution from $q'$, it could also stem from $q''$;
	conversely, the second occurrence of $q''$ could also be a substitution from $q'$ instead of being a faithful copy of its first occurrence.}
	}
	\label{fig:substitution-unmodelled}
\end{figure}

\begin{figure*}[h]
	\centering
	\begin{subfigure}{.49\textwidth}
	    \def\svgwidth{\textwidth}
	    \small
	    \input{images/substitution-Time=discrete-Source=majority-Past=last_bin-Durl=all.pdf_tex}
	    \caption{Source must be majority in preceding bin, destination can be anything}
	    \label{fig:substitution-modelled-majority-all}
	\end{subfigure}
	~
	\begin{subfigure}{.49\textwidth}
	    \def\svgwidth{\textwidth}
	    \small
	    \input{images/substitution-Time=discrete-Source=majority-Past=last_bin-Durl=exclude_past.pdf_tex}
	    \caption{Source must be majority in preceding bin, destination must not appear in preceding bin}
	    \label{fig:substitution-modelled-majority-exclude_past}
	\end{subfigure}

	\begin{subfigure}{.49\textwidth}
	    \def\svgwidth{\textwidth}
	    \small
	    \input{images/substitution-Time=discrete-Source=all-Past=last_bin-Durl=all.pdf_tex}
	    \caption{Source can be anything, destination can be anything\\\hfill} % \\\hfill to add a line, aligning with the other panels which have two-line captions
	    \label{fig:substitution-modelled-all-all}
	\end{subfigure}
	~
	\begin{subfigure}{.49\textwidth}
	    \def\svgwidth{\textwidth}
	    \small
	    \input{images/substitution-Time=discrete-Source=all-Past=last_bin-Durl=exclude_past.pdf_tex}
	    \caption{Source can be anything, destination must not appear in preceding bin}
	    \label{fig:substitution-modelled-all-exclude_past}
	\end{subfigure}
	\caption{\newtext{
	{\bf Substitution models.}
	Substitutions inferred by four models in the situation introduced by Fig.~\ref{fig:substitution-unmodelled}.
	Each of these models uses bins spanning 1 day aligned to midnight (see the main text for a complete description of parameters).
	In the top left panel~(a), $q$ holds the majority in the first bin and is considered the unique basis for $q'$ in bin~2.
	$q'$ and $q''$ have equal maximum frequency in bin~2 however, so both are sources of substitutions towards bin~3.
	In the top right panel~(b), quotes that appear in the preceding bin cannot be the target of a substitution; this removes two substitutions compared to panel~(a).
	In the bottom left panel~(c), the majority constraint is lifted compared to panel~(a), making $q''$ in bin~1 a candidate source for $q'$ in bin~2.
	In the bottom right panel~(d), the majority constraint is also lifted compared to panel~(a) (adding the same $q'' \rightarrow q'$ substitution as in panel~(c)), and the excluded-past constraint is added as in panel~(b) (removing the two same substitutions from bin~2 to bin~3 as in panel~(b)).
	If the bins were extended to the beginning of the quotation family, the excluded-past constraint would also remove the $q' \rightarrow q$ substitution from bin~2 to bin~3.
	In all four panels, a background rectangle or square indicates the quotation is the source of a substitution.
	A thick border on that rectangle or square indicates the quotation was selected because it has maximum frequency.}
	}
    \label{fig:substitution-modelled}
\end{figure*}

>>>>

\begin{figure}[h]
    \centering
	\def\svgwidth{\linewidth}
	\small
	\input{images/substitution-unmodelled.pdf_tex}
	\caption{{\bf Possible paths from occurrence to occurrence.}
	\newtext{$q$, $q'$ and $q''$ are three quotation variants belonging to the same cluster.
	$q$ and $q''$ differ by two words, but $q'$ differs from both $q$ and $q''$ by one word.
	The second occurrence of $q$ can safely be considered a faithful copy of the first, but the occurrences of $q'$ and $q''$ are uncertain:
	while the first occurrence of $q'$ is most likely a substitution from $q$, it could also stem from $q''$;
	conversely, the second occurrence of $q''$ could also be a substitution from $q'$ instead of being a faithful copy of its first occurrence.}
	}
	\label{fig:substitution-unmodelled}
\end{figure}

\begin{figure*}[h]
	\centering
	\begin{subfigure}{.49\textwidth}
	    \def\svgwidth{\textwidth}
	    \small
	    \input{images/substitution-Time=discrete-Source=majority-Past=last_bin-Durl=all.pdf_tex}
	    \caption{Source must be majority in preceding bin, destination can be anything}
	    \label{fig:substitution-modelled-majority-all}
	\end{subfigure}
	\begin{subfigure}{.49\textwidth}
	    \def\svgwidth{\textwidth}
	    \small
	    \input{images/substitution-Time=discrete-Source=majority-Past=last_bin-Durl=exclude_past.pdf_tex}
	    \caption{Source must be majority in preceding bin, destination must not appear in preceding bin}
	    \label{fig:substitution-modelled-majority-exclude_past}
	\end{subfigure}

	\begin{subfigure}{.49\textwidth}
	    \def\svgwidth{\textwidth}
	    \small
	    \input{images/substitution-Time=discrete-Source=all-Past=last_bin-Durl=all.pdf_tex}
	    \caption{Source can be anything, destination can be anything\\\hfill} % \\\hfill to add a line, aligning with the other panels which have two-line captions
	    \label{fig:substitution-modelled-all-all}
	\end{subfigure}
	\begin{subfigure}{.49\textwidth}
	    \def\svgwidth{\textwidth}
	    \small
	    \input{images/substitution-Time=discrete-Source=all-Past=last_bin-Durl=exclude_past.pdf_tex}
	    \caption{Source can be anything, destination must not appear in preceding bin}
	    \label{fig:substitution-modelled-all-exclude_past}
	\end{subfigure}
	\caption{\newtext{
	{\bf Substitution models.}
	Substitutions inferred by four models in the situation introduced by Fig.~\ref{fig:substitution-unmodelled}.
	Each of these models uses bins spanning 1 day aligned to midnight (see the main text for a complete description of parameters).
	In the top left panel~(a), $q$ holds the majority in the first bin and is considered the unique basis for $q'$ in bin~2.
	$q'$ and $q''$ have equal maximum frequency in bin~2 however, so both are sources of substitutions towards bin~3.
	In the top right panel~(b), quotes that appear in the preceding bin cannot be the target of a substitution; this removes two substitutions compared to panel~(a).
	In the bottom left panel~(c), the majority constraint is lifted compared to panel~(a), making $q''$ in bin~1 a candidate source for $q'$ in bin~2.
	In the bottom right panel~(d), the majority constraint is also lifted compared to panel~(a) (adding the same $q'' \rightarrow q'$ substitution as in panel~(c)), and the excluded-past constraint is added as in panel~(b) (removing the two same substitutions from bin~2 to bin~3 as in panel~(b)).
	If the bins were extended to the beginning of the quotation family, the excluded-past constraint would also remove the $q' \rightarrow q$ substitution from bin~2 to bin~3.
	In all four panels, a background rectangle or square indicates the quotation is the source of a substitution.
	A thick border on that rectangle or square indicates the quotation was selected because it has maximum frequency.}
	}
    \label{fig:substitution-modelled}
\end{figure*}
